### 2015-02-20 fundamentals/impl.tex
deleted confusing, out of place sentence
weird grammar

Quality assurance is an on-going process throughout the entire life of the
software. Since \Cyclus modeling decisions are made
by third party archetype developers or users, the most important feature of
\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond
the scope of the kernel.

Verification may be defined as the question, ``Is \Cyclus being built correctly?''
To answer this question, we turn to the software development of notions of testing,
documentation, version control, style guidelines, and continuous integration.
This suite of process controls supplies mechanism for reliable and reproducible
software. The impetus to implement these controls correctly is particularly strong in a scientific
context because of the emphasis on reproducibility and provenance. These verification techniques are
discussed individually in the sections that follow.

>>>>

Since \Cyclus modeling decisions are made
by third party archetype developers or users, the most important feature of
\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond
the scope of the kernel.

Verification may be defined as the question, ``Is \Cyclus being built correctly?''
To answer this question, \Cyclsu relies on software development best practices
such as testing,
documentation, version control, style guidelines, and continuous integration.
This suite of process controls supplies mechanism for reliable and reproducible
software. The impetus to implement these controls correctly is particularly strong in a scientific
context because of the emphasis on reproducibility and provenance. These verification techniques are
discussed individually in the sections that follow.
